Reduced growth due to belowground sink limitation is not fully explained by reduced photosynthesis

### 2016-07-11 manuscript/manuscript_pve.Rmd
added cites, still missing A and growth decouple cites

\
Most current models of plant growth are based on the physical principle of mass balance: C entering the plant through photosynthesis must be balanced by C loss to respiration and C allocation to growth and storage. Plant growth is thus predicted as the outcome of the processes of photosynthesis, respiration and allocation.  It is easy to see how source-limited growth can be implemented in such models: increasing source activity increases photosynthetic C uptake, flowing through to increased growth. It is less easy to know how to implement sink limitation of growth in such models, because it requires that we know whether, and how, sink limitation influences the contributing processes of photosynthesis, respiration and allocation. It has been suggested that sink limitation affects the C balance by causing a down-regulation of photosynthetic rate, possibly mediated by carbohydrate accumulation (refs), but there is also evidence that photosynthesis and growth are decoupled under sink limitation (refs), suggesting that other processes must also be affected.

>>>>

\
Most current models of plant growth are based on the physical principle of mass balance: C entering the plant through photosynthesis must be balanced by C loss to respiration and C allocation to growth and storage. Plant growth is thus predicted as the outcome of the processes of photosynthesis, respiration and allocation.  It is easy to see how source-limited growth can be implemented in such models: increasing source activity increases photosynthetic C uptake, flowing through to increased growth. It is less easy to know how to implement sink limitation of growth in such models, because it requires that we know whether, and how, sink limitation influences the contributing processes of photosynthesis, respiration and allocation. It has been suggested that sink limitation affects the C balance by causing a down-regulation of photosynthetic rate, possibly mediated by carbohydrate accumulation [@arp1991effects; @paul2001sink;@ainsworth2004testing; @ronchi2006growth; @nebauer2011photosynthesis], but there is also evidence that photosynthesis and growth are decoupled under sink limitation *(refs)*, suggesting that other processes must also be affected.
